A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Edits - bigger ticks

Next, we reincorporate popularity by modifying how we search for nearest
neighbors in concept space. Instead of simply ranking neighbors by distance, we
now rank by distance divided by $\rho$.  In this context, having defined
popularity as the logorithm of node degree reduces the liklihood that one or two
very popular items will always appear as the best recommendations when using
this weighted ranking policy.

The third way in which popularity is used is determining the number
recommendations alotted per product. We assume that a popular product in one
catalogue is likely to be a popular product in another catalogue. Specifically,
the number of predicted inter-catalogue recommendations predicted per item is
made directly proportional to the item's value of $\rho$.

This assumption is corroborated by the data. The following histogram shows the
number of gold-standard recommendations associated with the top 25 most popular
items, ranked by their value of $\rho$. The histogram also includes the
distribution of predicted recommendations for these items by the
$LatentFeatureRecommender$ both with and without popularity mechanisms. With
popularity, the predictions follow a similar distribution to that of the
gold-standard recommendations. Without popularity, the recommendations are
scattered more uniformly over the thousands of items of each catalogue such that
the number of times these 25 items are recommended is significantly smaller
(barely visible in the plot). This is because the recommendations are based
solely on similarity in concept space (after mapping) and popular items are not
inherently more similar to other items. Importantly, the
$LatentFeatureRecommender$ {\em without popularity} still outperforms the
$ContentBasedRecommender$ demonstrating that while popularity is important, it
is only one of several features that useful in choosing good inter-catalogue
recommendations.

>>>>

Next, we reincorporate popularity by modifying how we search for nearest
neighbors in concept space. Instead of simply ranking neighbors by distance, we
now rank by distance divided by $\rho$, thus promoting popular items.  In this
context, having defined popularity as the logorithm of node degree reduces the
liklihood that one or two very popular items will always appear as the best
recommendations when using this weighted ranking policy.

The third way in which popularity is used is determining the number of
recommendations alotted per product. We assume that a popular product in one
catalogue is likely to be a popular product in another catalogue. Specifically,
the number of predicted inter-catalogue recommendations predicted per item is
made directly proportional to the item's value of $\rho$.

This assumption is corroborated by the data. The following histogram shows the
number of gold-standard recommendations associated with the top 25 most popular
items, as determinded by $\rho$. The histogram also includes the
distribution of predicted recommendations for these items by the
$LatentFeatureRecommender$ both with and without popularity mechanisms. With
popularity, the predictions follow a similar distribution to that of the
gold-standard recommendations. Without popularity, the recommendations are
scattered more uniformly over the thousands of items of each catalogue such that
the number of times these 25 items are recommended is significantly smaller
(barely visible in the plot). This is because the recommendations are based
solely on similarity in concept space (after mapping) and popular items are not
inherently more similar to other items. Importantly, the
$LatentFeatureRecommender$ {\em without popularity} still outperforms the
$ContentBasedRecommender$, demonstrating that while popularity is important, it
is only one of several features that are useful in choosing good inter-catalogue
recommendations.
